%-------------------------
%~~~~~~~~~~~~~~~~~~~~~~~~~
% CV — Samrat Dey
% Focus: Cybersecurity | Red Teaming | Security Auditing
% Last Updated: 2026-04-07
%~~~~~~~~~~~~~~~~~~~~~~~~~
%-------------------------

\documentclass[11pt,a4paper]{article}

%----- Packages -----
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage[most]{tcolorbox}

%----- Page Setup -----
\geometry{left=1.4cm, top=1.2cm, right=1.4cm, bottom=1.2cm}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\tabcolsep}{0in}
\raggedright

%----- Accent Color -----
\definecolor{accent}{HTML}{2E86AB}
\definecolor{accentdark}{HTML}{1a5c7a}
\definecolor{lightgray}{HTML}{F4F4F4}
\definecolor{rulegray}{HTML}{CCCCCC}

%----- Section Formatting -----
\titleformat{\section}{
  \vspace{-6pt}\large\bfseries\color{accent}\raggedright
}{}{0em}{}[{\color{accent}\titlerule[1.2pt]}\vspace{-5pt}]

%----- tcolorbox style -----
\tcbset{
  frame code={},
  left=2pt, right=2pt, top=2pt, bottom=2pt,
  colback=lightgray, colframe=white,
  width=\dimexpr\textwidth\relax,
  boxsep=3pt, arc=2pt, outer arc=2pt,
}

%----- Custom Column Types -----
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}

%----- Custom Commands -----
\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\normalsize #1} & \small\textit{#4} \\
    \small\textit{#3} & \small #2 \\
  \end{tabular*}
  \vspace{-2pt}
}

\newcommand{\resumeProject}[3]{
  \vspace{3pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\normalsize #1} & \small #3 \\
    \small\textit{#2} & \\
  \end{tabular*}
  \vspace{-2pt}
}

\newcommand{\resumePOR}[3]{
  \vspace{-6pt}\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} \hspace{1mm} \small{#2} & \small\textit{#3}
  \end{tabular*}
  \vspace{-3pt}
}

\newcommand{\resumeSkillItem}[2]{
  \item{\textbf{\small #1:}\hspace{1mm}\small #2}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{1mm}}
\newcommand{\resumeItemListStart}{%
  \begin{justify}
  \begin{itemize}[leftmargin=3.5ex, rightmargin=1ex, itemsep=0.5pt, labelsep=1.5mm]
  \small
}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\resumeSkillListStart}{\begin{itemize}[leftmargin=*,itemsep=2pt,rightmargin=2ex]}
\newcommand{\resumeSkillListEnd}{\end{itemize}\vspace{-2mm}}

\renewcommand{\labelitemi}{\textcolor{accent}{\small$\bullet$}}
\renewcommand{\labelitemii}{\textcolor{accent}{\small$\circ$}}

%----- Personal Info -----
\newcommand{\name}{Samrat Dey}
\newcommand{\phone}{9382919726}
\newcommand{\emaila}{samratdey.career@gmail.com}
\newcommand{\github}{3rr0r-505}
\newcommand{\linkedin}{samratd3y}
\newcommand{\portfolio}{me.5pyd3r.org}

%=========================================
\begin{document}
%=========================================

%---------- HEADER ----------
{
  \centering
  {\LARGE\bfseries \name} \\[4pt]
  \small
  \textcolor{accent}{\faPhone}\ +91-\phone \hspace{4pt}
  \textcolor{accent}{\faEnvelope}\ \href{mailto:\emaila}{\emaila} \hspace{4pt}
  \textcolor{accent}{\faGithub}\ \href{https://github.com/\github}{\github} \hspace{4pt}
  \textcolor{accent}{\faLinkedin}\ \href{https://www.linkedin.com/in/\linkedin/}{in/\linkedin} \hspace{4pt}
  \textcolor{accent}{\faGlobe}\ \href{https://\portfolio}{\portfolio} \\[4pt]
  % ================= M.Tech line (uncomment when admitted): =================
  %\textit{\small M.Tech {\large\textbf{---}} Information Security \hspace{4pt}$\bullet$\hspace{4pt} B.Tech {\large\textbf{---}} Computer Science \hspace{4pt}$\bullet$\hspace{4pt} Penetration Testing \& Red Team Enthusiast}\\[2pt]
  % ================= B.Tech line (active): =================
  \textit{\small B.Tech {\large\textbf{---}} Computer Science \hspace{4pt}$\bullet$\hspace{4pt} Penetration Testing \& Red Team Enthusiast}\\[2pt]
  \par
}

\vspace{1mm}
\noindent\textcolor{rulegray}{\rule{\linewidth}{0.4pt}}
\vspace{-3mm}

%---------- SUMMARY ----------
\section{Summary}
\justify\small
B.Tech Computer Science graduate with hands-on experience in cybersecurity, penetration testing, and vulnerability analysis across lab, academic, and cloud environments. Proficient in Linux security, network protocol analysis, Python-based security scripting, and SIEM-based threat monitoring using Wazuh. Experienced in building offensive security tools, analyzing real-world attack techniques, and evaluating system and application security controls, targeting roles in red teaming, security auditing, and enterprise security assessment.

\vspace{-1mm}

%---------- EDUCATION ----------
\section{Education}
\setlength{\tabcolsep}{5pt}
\renewcommand{\arraystretch}{1.15}
\small
\begin{tabularx}{\textwidth}{|c|C|c|c|}
  \hline
  \textbf{Degree / Certificate} & \textbf{Institute / Board} & \textbf{Score} & \textbf{Year} \\
  \hline
  B.Tech. CSE & Adamas University, Kolkata & 8.77 CGPA & 2021--2025 \\
  \hline
  Senior Secondary (XII) & WBCHSE Board & 91.2\% & 2021 \\
  \hline
  Secondary (X) & WBBSE Board & 94.2\% & 2019 \\
  \hline
\end{tabularx}

%---------- EXPERIENCE ----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Cyber Security \& Ethical Hacking Intern}{\href{https://5pyd3r.is-a.dev/assets/certs/intern-2024.pdf}{\textcolor{accent}{Certificate}}}
    {NIELIT Haridwar, India}{Jul. 2024 -- Aug. 2024}
    \resumeItemListStart
      \item Performed hands-on vulnerability assessment and exploitation using Metasploit, Nmap, Searchsploit, and Sherlock against lab environments (Metasploitable, EternalBlue/DoublePulsar).
      \item Conducted adversary simulation on Android targets using msfvenom, AndroRAT, and StromBreaker; documented attack chains and mitigation strategies.
      \item Deployed and monitored Wazuh SIEM for threat detection, log correlation, and security event analysis in a simulated enterprise setup.
      \item Analyzed landmark malware campaigns (WannaCry, NotPetya, Stuxnet) to extract TTPs and map to MITRE ATT\&CK framework concepts.
      \item Completed structured offensive and defensive CTF challenges on TryHackMe, reinforcing practical exploitation and incident response skills.
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-5mm}

%---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

  % HoneyPott3r
  \resumeSubheading
    {HoneyPott3r --- Honeypot Vulnerability Assessment Framework}{\href{https://github.com/3rr0r-505/HoneyPott3r}{\textcolor{accent}{\faGithub\ GitHub}}}
    {Systematic security analysis framework targeting honeypot infrastructure.}{}
    \resumeItemListStart
      \item Designed and executed simulated attack scenarios --- detection evasion, log manipulation, privilege escalation, reverse exploitation, and DoS --- against Cowrie, Conpot, and Wordpot honeypots deployed in Docker on AWS EC2 (Debian).
      \item Conducted multi-vector vulnerability scanning using Trivy, Bandit, Safety-CLI, Nmap, Nikto, and WPScan; integrated Metasploit module lookups to map exploitable attack paths.
      \item Identified critical configuration weaknesses in SSH and HTTP honeypot deployments, proposing deception hardening and improved threat monitoring strategies.
      \item Stored attack telemetry in MongoDB and built an interactive web dashboard for real-time visualization and structured reporting.
      \item Published findings as a peer-reviewed research paper in IJPREMS (Mar. 2025).
    \resumeItemListEnd

  % KeySpy
  \resumeSubheading
    {KeySpy --- Endpoint Monitoring \& Keystroke Security Research Tool}{\href{https://github.com/3rr0r-505/KeySpy}{\textcolor{accent}{\faGithub\ GitHub}}}
    {Python-based endpoint risk analysis tool for keylogger and remote payload execution research.}{}
    \resumeItemListStart
      \item Simulated USB-based payload delivery and remote payload execution (RPE) scenarios in a controlled lab to evaluate endpoint detection and response (EDR) gaps.
      \item Captured keystrokes, active window context, and timestamps via \texttt{pynput}; implemented AES encryption for secure data storage and transmission, following security research best practices.
      \item Persisted collected telemetry in MongoDB Atlas and built a real-time web interface for event visualization and security control assessment.
    \resumeItemListEnd

  % HawkPro
  \resumeSubheading
    {HawkPro --- Linux System \& Process Monitor}{\href{https://github.com/3rr0r-505/HawkPro}{\textcolor{accent}{\faGithub\ GitHub}}}
    {Terminal-based real-time system monitoring tool built in C++ with ncurses, inspired by htop.}{}
    \resumeItemListStart
      \item Parsed the Linux \texttt{/proc} filesystem to display live CPU, memory, and per-process statistics in an interactive terminal UI.
      \item Implemented a modular C++ architecture with CMake; optimized polling intervals for minimal performance overhead, demonstrating low-level Linux system programming proficiency.
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5mm}

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\resumeSkillListStart
  \resumeSkillItem{Offensive Security Tools}
    {Metasploit, Nmap, Burp Suite, Nikto, WPScan, Searchsploit, Trivy, Bandit, Safety-CLI, msfvenom, Sherlock}
  \resumeSkillItem{Security \& Monitoring}
    {Wazuh SIEM, Wireshark, AndroRAT, StromBreaker, log analysis, threat detection, MITRE ATT\&CK}
  \resumeSkillItem{Programming \& Scripting}
    {Python (security scripting, automation), Go (network programming, TLS analysis), C/C++ (memory concepts, OOP, STL), Bash (scripting)}
  \resumeSkillItem{Web Technologies}
    {HTML, CSS, JavaScript (basic), web dashboard development}
  \resumeSkillItem{Cloud \& Platforms}
    {AWS EC2 (Debian), Docker, Git/GitHub, VMware, VirtualBox, VS Code}
  \resumeSkillItem{Databases}
    {MongoDB (Atlas, Compass), MySQL}
  \resumeSkillItem{Operating Systems}
    {Kali Linux, Ubuntu, Windows}
\resumeSkillListEnd

%---------- PUBLICATIONS ----------
\section{Publications}
\begin{itemize}[leftmargin=*, itemsep=2pt]
  \small\item A.~B.~Thakur, \textbf{S.~Dey}, S.~Rahman, and A.~Chaurasia,
  ``\textbf{HONEYPOTT3R: An Open-Source Multi-Layered Security Analysis Framework for Honeypot Vulnerability Assessment},''
  \textit{International Journal of Progressive Research in Engineering Management and Science (IJPREMS)},
  vol.~5, issue.~3, pp.~1723--1730, Mar.~2025.
  DOI: \href{https://www.doi.org/10.58257/IJPREMS39220}{\textcolor{accent}{10.58257/IJPREMS39220}}.
\end{itemize}
\vspace{-3mm}

%---------- CERTIFICATIONS ----------
\section{Certifications}
\resumeSubHeadingListStart
  \resumePOR{Jr. Penetration Tester}{--- TryHackMe}
    {\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-EVC7DTCYWJ.pdf}{\textcolor{accent}{View}}}
  \resumePOR{CompTIA Pentest+}{--- TryHackMe}
    {\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-9YN8F6SLAJ.pdf}{\textcolor{accent}{View}}}
  \resumePOR{Advent of Cyber 2024}{--- TryHackMe}
    {\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-KCYOBBMWKV.pdf}{\textcolor{accent}{View}}}
  \resumePOR{Introduction to Cyber Security}{--- TryHackMe}
    {\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-VDDWDT8NWY.pdf}{\textcolor{accent}{View}}}
  \resumePOR{Web Fundamentals}{--- TryHackMe}
    {\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-NLQ4QFBFJZ.pdf}{\textcolor{accent}{View}}}
  \resumePOR{Introduction to Cloud Semester 1}{--- AWS Educate}
    {\href{https://www.credly.com/badges/5c61ac7a-62f5-4728-954e-5d3fc481cc9b/public_url}{\textcolor{accent}{View}}}
  \resumePOR{Introduction to Cloud 101}{--- AWS Educate}
    {\href{https://www.credly.com/badges/d6837af8-9e13-47fc-b375-928fe63768f2/public_url}{\textcolor{accent}{View}}}
\resumeSubHeadingListEnd

%=========================================
\end{document}