%--------------------------------------------------------------------------------
% Resume — Samrat Dey
% Focus: Cybersecurity | Red Teaming | Security Auditing
% Last Updated: 2026-04-07
%--------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article}

%----- Packages -----
\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}

%----- Page Setup -----
\geometry{left=1.3cm, top=1.2cm, right=1.3cm, bottom=1.2cm}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\tabcolsep}{0in}
\raggedright
\pagenumbering{gobble}

%----- Accent Color -----
\definecolor{accent}{HTML}{2E86AB}
\definecolor{rulegray}{HTML}{CCCCCC}

%----- Section Formatting -----
\titleformat{\section}{
  \vspace{-4pt}\large\bfseries\color{accent}\raggedright
}{}{0em}{}[{\color{accent}\titlerule[1.2pt]}\vspace{-3pt}]

\titlespacing*{\section}{0pt}{9pt}{5pt}

%----- Bullet style -----
\renewcommand{\labelitemi}{\textcolor{accent}{\small$\bullet$}}

%----- Custom Column Types -----
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

%----- Personal Info -----
\newcommand{\name}{Samrat Dey}
\newcommand{\phone}{9382919726}
\newcommand{\emaila}{samratdey.career@gmail.com}
\newcommand{\github}{3rr0r-505}
\newcommand{\linkedin}{samratd3y}
\newcommand{\portfolio}{me.5pyd3r.org}

%=========================================
\begin{document}
%=========================================

%---------- HEADER ----------
{
  \centering
  {\LARGE\bfseries \name} \\[5pt]
  \small
  \textcolor{accent}{\faPhone}\ +91-\phone \hspace{4pt}
  \textcolor{accent}{\faEnvelope}\ \href{mailto:\emaila}{\emaila} \hspace{4pt}
  \textcolor{accent}{\faGithub}\ \href{https://github.com/\github}{\github} \hspace{4pt}
  \textcolor{accent}{\faLinkedin}\ \href{https://www.linkedin.com/in/\linkedin/}{in/\linkedin} \hspace{4pt}
  \textcolor{accent}{\faGlobe}\ \href{https://\portfolio}{\portfolio} \\[4pt]
  % ================= M.Tech line (uncomment when admitted): =================
  %\textit{\small M.Tech {\large\textbf{---}} Information Security \hspace{4pt}$\bullet$\hspace{4pt} B.Tech {\large\textbf{---}} Computer Science \hspace{4pt}$\bullet$\hspace{4pt} Penetration Testing \& Red Team Enthusiast}\\[2pt]
  % ================= B.Tech line (active): =================
  \textit{\small B.Tech {\large\textbf{---}} Computer Science \hspace{4pt}$\bullet$\hspace{4pt} Penetration Testing \& Red Team Enthusiast} \\[2pt]
  \par
}

\vspace{1mm}
\noindent\textcolor{rulegray}{\rule{\linewidth}{0.4pt}}
\vspace{-2mm}

%---------- SUMMARY ----------
\section{Professional Summary}
\small
B.Tech Computer Science graduate with hands-on experience in cybersecurity, penetration testing, and vulnerability analysis across lab, academic, and cloud environments. Proficient in Linux security, network protocols (TCP/IP, DNS, HTTP), Python-based security scripting, and SIEM-based threat monitoring using Wazuh. Targeting roles in red teaming, security auditing, or enterprise security assessment.

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
\small
\textbf{Offensive Security Tools:} Metasploit, Nmap, Burp Suite, Nikto, WPScan, Searchsploit, Trivy, Bandit, Safety-CLI, msfvenom, Sherlock \\[3pt]
\textbf{Security \& Monitoring:} Wazuh SIEM, Wireshark, log analysis, threat detection, MITRE ATT\&CK \\[3pt]
\textbf{Programming \& Scripting:} Python (security scripting, automation), Go, C/C++, Bash \\[3pt]
\textbf{Cloud \& Platforms:} AWS EC2, Docker, Git/GitHub, VMware, VirtualBox, VS Code \\[3pt]
\textbf{Databases:} MongoDB (Atlas, Compass), MySQL \hspace{10pt} \textbf{OS:} Kali Linux, Ubuntu, Windows

%---------- EXPERIENCE ----------
\section{Experience}
\noindent
\begin{tabularx}{\textwidth}{L R}
  \textbf{Cyber Security \& Ethical Hacking Intern} & \textit{Jul. 2024 -- Aug. 2024} \\
  \textit{NIELIT Haridwar, India} & \href{https://5pyd3r.is-a.dev/assets/certs/intern-2024.pdf}{\textcolor{accent}{Certificate}} \\
\end{tabularx}
\vspace{3pt}
\begin{itemize}[leftmargin=3.5ex, itemsep=2.5pt, topsep=0pt]
  \small
  \item Performed vulnerability assessment and exploitation using Metasploit, Nmap, Searchsploit, and Sherlock against lab environments (Metasploitable, EternalBlue/DoublePulsar).
  \item Conducted adversary simulation on Android targets (msfvenom, AndroRAT, StromBreaker); deployed and monitored Wazuh SIEM for threat detection and log correlation.
  \item Analyzed landmark malware campaigns (WannaCry, NotPetya, Stuxnet) to extract TTPs and map to MITRE ATT\&CK; completed structured CTF challenges on TryHackMe.
\end{itemize}

%---------- PROJECTS ----------
\section{Projects}

% HoneyPott3r
\noindent
\begin{tabularx}{\textwidth}{L R}
  \textbf{HoneyPott3r --- Honeypot Vulnerability Assessment Framework} & \href{https://github.com/3rr0r-505/HoneyPott3r}{\textcolor{accent}{\faGithub\ GitHub}} \\
\end{tabularx}
\vspace{1pt}
\textit{\small Systematic security analysis framework targeting honeypot infrastructure (Docker, AWS EC2).}
\begin{itemize}[leftmargin=3.5ex, itemsep=2.5pt, topsep=3pt]
  \small
  \item Executed simulated attack scenarios (detection evasion, privilege escalation, reverse exploitation, DoS) against Cowrie, Conpot, and Wordpot honeypots; conducted multi-vector scanning using Trivy, Bandit, Nmap, Nikto, and WPScan.
  \item Identified critical configuration weaknesses; stored telemetry in MongoDB with interactive dashboard for reporting. Findings published as peer-reviewed paper in IJPREMS (Mar. 2025).
\end{itemize}

\vspace{5pt}
% KeySpy
\noindent
\begin{tabularx}{\textwidth}{L R}
  \textbf{KeySpy --- Endpoint Monitoring \& Keystroke Security Research Tool} & \href{https://github.com/3rr0r-505/KeySpy}{\textcolor{accent}{\faGithub\ GitHub}} \\
\end{tabularx}
\vspace{1pt}
\textit{\small Python-based endpoint risk analysis tool for keylogger and remote payload execution (RPE) research.}
\begin{itemize}[leftmargin=3.5ex, itemsep=2.5pt, topsep=3pt]
  \small
  \item Simulated USB-based payload delivery and RPE scenarios to evaluate EDR gaps; implemented AES encryption for secure data storage and built a real-time web interface for event visualization.
\end{itemize}

\vspace{5pt}
% HawkPro
\noindent
\begin{tabularx}{\textwidth}{L R}
  \textbf{HawkPro --- Linux System \& Process Monitor} & \href{https://github.com/3rr0r-505/HawkPro}{\textcolor{accent}{\faGithub\ GitHub}} \\
\end{tabularx}
\vspace{1pt}
\textit{\small Terminal-based real-time system monitoring tool built in C++ with ncurses, inspired by htop.}
\begin{itemize}[leftmargin=3.5ex, itemsep=2.5pt, topsep=3pt]
  \small
  \item Parsed Linux \texttt{/proc} filesystem to display live CPU, memory, and per-process statistics in an interactive terminal UI; modular CMake architecture with optimized polling for minimal overhead.
\end{itemize}

%---------- EDUCATION ----------
\section{Education}
\noindent
\begin{tabularx}{\textwidth}{L R}
  \textbf{Adamas University, Kolkata} & \textit{2021 -- 2025} \\
  \textit{B.Tech in Computer Science and Engineering} & \textit{CGPA: 8.77} \\
\end{tabularx}

%---------- PUBLICATIONS ----------
\section{Publications}
\small
\textbf{HONEYPOTT3R}: An Open-Source Multi-Layered Security Analysis Framework for Honeypot Vulnerability Assessment \\[2pt]
\textit{IJPREMS}, vol. 5, issue 3, pp. 1723--1730, Mar. 2025 \hfill DOI: \href{https://doi.org/10.58257/IJPREMS39220}{\textcolor{accent}{10.58257/IJPREMS39220}}

%---------- CERTIFICATIONS ----------
\section{Certifications}
\small
\textbf{TryHackMe:}
\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-9YN8F6SLAJ.pdf}{\textcolor{accent}{CompTIA Pentest+}},
\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-EVC7DTCYWJ.pdf}{\textcolor{accent}{Jr. Penetration Tester}},
\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-KCYOBBMWKV.pdf}{\textcolor{accent}{Advent of Cyber 2024}},
\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-VDDWDT8NWY.pdf}{\textcolor{accent}{Intro to Cyber Security}},
\href{https://tryhackme-certificates.s3-eu-west-1.amazonaws.com/THM-NLQ4QFBFJZ.pdf}{\textcolor{accent}{Web Fundamentals}} \\[3pt]
\textbf{AWS Educate:}
\href{https://www.credly.com/badges/d6837af8-9e13-47fc-b375-928fe63768f2/public_url}{\textcolor{accent}{Introduction to Cloud 101}},
\href{https://www.credly.com/badges/5c61ac7a-62f5-4728-954e-5d3fc481cc9b/public_url}{\textcolor{accent}{Cloud Semester 1}}

%=========================================
\end{document}